%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\tracingstats=0
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Shreyas Atre} \\ \vspace{1pt}
    \small +91 7020418098 $|$ \href{mailto:shreyasatre16@gmail.com}{\underline{shreyasatre16@gmail.com}} $|$ 
    \href{https://linkedin.com/in/atreshreyas}{\underline{linkedin.com/in/atreshreyas}} $|$
    \href{https://github.com/SAtacker}{\underline{github.com/SAtacker}} $|$
    \href{https://satacker.github.io/}{\underline{https://satacker.github.io/}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Veermata Jijabai Technological Institute}{Mumbai, India}
      {BTech. in Electronics and Telecommunications Engineering}{Aug. 2019 -- Aug. 2023}
  \resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CNCF and Linux Foundation Intern}{September 2021 -- November 2021}
      {WasmEdge Runtime}{Remote}
      \resumeItemListStart
        \resumeItem{WasmEdge is a lightweight, high-performance, and extensible WebAssembly runtime for cloud native, edge, and decentralized applications.}
        \resumeItem{ It powers serverless apps, embedded functions, microservices, smart contracts, and IoT devices.}
        \resumeItem{Developed a C-Extension for the Python SDK that supports near native speeds.}
        \resumeItem{Developed unit-tests and established benchmarks for the C-Extension of Python SDK.}
        \resumeItem{Supported multiple operation modes of WasmEdge Runtime in C-Extension for Python-API.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Google Summer of Code}{June 2021 -- August 2021}
      {BeagleBoard.org}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and implemented a dashboard using FTXUI to aid the low level configurations in linux and some specifics to beaglebone boards using Modern CPP}
        \resumeItem{Used userspace's IOCTL calls, Sockets for adding routes and deleting them.}
        \resumeItem{Cross Compilation for ARM architecture using clang and gnu tool-chain and used build file generator CMake}
    \resumeItemListEnd

    \resumeSubheading
      {Munga Innovations}{March 2020 - June 2020}
      {Embedded and AI intern}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Developed a Image Classifier based on the Inception v3 for detection of unnecessary matter on Solar Panels, light enough to run on resource constrained systems.}
        \resumeItem{Integrated the CNN on Rasp. PI 4 with Espressif's micro-controller ESP32 for the complete cleaning cycle of the cleaning bot.}
        \resumeItem{Designed a back-end for the above mentioned cleaning process on ESP32 with integration to firebase using esp-idf API for client side web interface.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{DRV8305 Driver} $|$ \emph{C}}{August 2021 -- September 2021}
            \resumeItemListStart
                \resumeItem{Texas Instruments's DRV8305 has support for R/W of it's Control and Status Registers.}
                \resumeItem{Implemented a driver for Espressif's ESP32 to establish Communication over SPI with R/W to the mentioned registers}
                \resumeItem{Developed on top of freeRTOS and Esp-IDF tool-chain.}
            \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{PID Tuning GUI Plotter} $|$ \emph{Qt, Modern C++}}{January 2021 -- March 2021}
          \resumeItemListStart
                \resumeItem{Developed a Cross Platform Application to plot and tune the PID Control parameters for Wall-E Robot}
                \resumeItem{Used Boost ASIO for networking and Threads for concurrency, and Qt SIGNALS for internal Queue handling}
                \resumeItem{Automated builds and Added material UI for the appearance and extensive documentation for the same.}
          \resumeItemListEnd
% \newpage % ---------------------------------------------------------
      \resumeProjectHeading
          {\textbf{Imitecio | Human Pose Estimation Based Application} $|$ \emph{Tensorflow 1.1x}}{June 2020 -- July 2020}
          \resumeItemListStart
                \resumeItem{Human Pose estimation has been around for a while and inspiration was taken from the same to make a game based on it.}
                \resumeItem{Several CNN architectures along with various bottom-up and top-down approaches for devising the keypoints were studied and transfer learning on pre-trained models was accomplished.}
                \resumeItem{Used Tensorflow Lite's Interpreter to get the keypoints from Google's PoseNet Model and mapped the same using OpenCV over the frames.}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd
% ------------------------Responsibilities
\section{Responsibilities}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Society of Robotics and Automation}{2019 -- Present}
            {Software Head}{VJTI, India}
            \resumeItemListStart
            \resumeItem{Taught various robotics concepts including Motor Control using MCPWM unit on ESP32 for Self Balancing and Line Following Bot}
            \resumeItem{Mentored Juniors for the Eklavya Summer Mentorship Program for projects like Audio Noise Reduction using Machine Learning based approaches, TUI for Email Client, Audio Router using Espressf's ESP32, etc.}
            \resumeItem{Taught Convolution in Computer Vision and various advanced Python Programming Concepts and Computer Vision Modules like OpenCV.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\section{Competitions}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Eyantra Robotics Competition by IIT-B} $|$ \emph{ROS Melodic, Python 2,Drone}}{October 2020 -- March 2021}
            \resumeItemListStart
                \resumeItem{Successfully completed all the stages of Competition and Applied Control Systems on a UAV (Drone)}
                \resumeItem{Featured HAAR Cascade using OpenCV for detection of landing markers and Implemented path planning algorithms and obstacle avoidance}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{SRA Auto Sim Competition} $|$ \emph{ROS Melodic, Python 2,Line Follower}}{December 2020}
            \resumeItemListStart
                \resumeItem{The competition consisted in implementing algorithm for Line Follower Bot and navigating through a series of puzzling areas which makes it much challenging.}
                \resumeItem{Implemented PID Controller for which we were awarded II Prize.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++ (11, 14, 17), Python (2 \& 3), Bash \& Shell} \\
     \textbf{Frameworks}{: Qt for Cross Platform Development, Build Systems and Toolkits, ML frameworks like PyTorch, TF, WebAssembly tools like WasmEdge} \\
     \textbf{Developer Tools}{: Git, Docker, Singularity, freeRTOS, ROS, eLinux, ESP32, SBCs like BeagleBoard} \\
     \textbf{Libraries}{: Boost ASIO, Boost Python, Python C extension API, FTXUI,  C++ Standard Headers}
    }}
 \end{itemize}
    
\end{document}
